Off-target spray particle movement

### 2021-07-15 manuscript.Rmd
bv

---
title: "Spray particle drift"
author: Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo Werle
date: "`r format(Sys.Date())`"
documentclass: article
linestretch: 2
abstract: "BACKGROUND: "
papersize: "a4"
mainfont: Arial
#monofont: "Arial"
#monofontoptions: "Scale=0.7"
fontsize: "12pt"
geometry:
  margin = 2.54cm
csl: pms.csl
bibliography: biblio.bib
output:
  pdf_document: 
      latex_engine: xelatex
      keep_tex: true
      toc_depth: 4
      number_sections: true

@@

@@

## Experimental sites

Field experiments were conducted in three locations: North Platte, NE (geographic coordinates) on September 11-12/2021; Arlington, WI (geographic coordinates) on September 15-16/2021; and city, MO (geographic coordinates) on September 18-20/2021. In NE, WI, and MO, applications were made on bare ground, corn stubble (XX cm height) and ????, respectively. The fields were flat and with no surrounding trees. Samples were processed and analyzed at the Pesticide Application Technology Laboratory of the University of Nebraska-Lincoln located in North Platte, Nebraska.

@@

@@

## Application and field layout

@@

## Dye quantification

@@

@@

### Spray solution deposition at upwind and inswath

@@

### Spray solution deposition at downwind

@@

The area under the curve (AUC) was used to validate the linear models. The spray solution deposition across distances within an experimental unit were used to calculate the absolute AUC value. The AUC was performed with *audps* function from the "agricolae" package. The AUC is commonly used for plant disease progress [@meenaAreaDiseaseProgress2011; @simkoAreaDiseaseProgress2011] but has been used to calculate herbicide injury @striegelSpraySolutionPH2021. Data was fitted to a mixed model using *brm* function. Treatments were the fixed effects and blocks nested within location random effects. Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from the "emmeans" package. Treatment means were compared using Bayes Factor (BF) as above-mentioned.

### Dv, Relative Span

>>>>

---
title: "Off-target spray particle movement"
author: 
  - "Rodrigo Werle"
  - "Bruno C Vieira"
  - "Maxwel C. Oliveira"
  - "Guilherme Alves"
  - "Greg Kruger"
date: "`r format(Sys.Date())`"
documentclass: article
linestretch: 2
abstract: "BACKGROUND: "
papersize: "a4"
mainfont: Arial
#monofont: "Arial"
#monofontoptions: "Scale=0.7"
fontsize: "12pt"
geometry:
  margin = 2.54cm
csl: pms.csl
bibliography: biblio.bib
output:
  pdf_document: 
      latex_engine: xelatex
      keep_tex: true
      toc_depth: 4
      number_sections: true

@@

Integrate pest management The off-target particle movement

The introduction of

The objective of this study was to compare

@@

@@

Field experiments were conducted in three locations: North Platte, NE (geographic coordinates) on September 11-12/2021; Arlington, WI (geographic coordinates) on September 15-16/2021; and city, MO (geographic coordinates) on September 18-20/2021. Applications were made on bare ground, corn stubble (XX cm height) and ???? in NE, WI, and MO, respectively. The fields were flat and with no surrounding trees. Samples were processed and analyzed at the Pesticide Application Technology Laboratory of the University of Nebraska-Lincoln located in North Platte, Nebraska.

@@

### Application and field layout

@@

### Dye quantification

@@

## Greenhouse study

A completely randomized design

@@

### Field study

#### Spray solution deposition at upwind and inswath

@@

#### Spray solution deposition at downwind

@@

The area under the curve (AUC) was used to validate the linear models. The spray solution deposition across distances within an experimental unit were used to calculate the absolute AUC value. The AUC was performed with *audps* function from the "agricolae" package. The AUC is commonly used for plant disease progress [@meenaAreaDiseaseProgress2011; @simkoAreaDiseaseProgress2011] but has been used to calculate herbicide injury [@striegelSpraySolutionPH2021]. Data was fitted to a mixed model using *brm* function. Treatments were the fixed effects and blocks nested within location random effects. Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior summaries and treatment means were estimated and compared using Bayes Factor (BF) as above-mentioned.

## Greenouse study

The Dv(10,50,90), RS, and % drifable fines was fitted to a Bayesian linear mixed model using *brm* function. In the models, solution and nozzle were set as fixed effects. Model family was hurdle gamma and prior distribution was set to student-t with mean 0.5, standard deviation 1 and 2 degrees of freedom. For each response variable, two models were fitted: with and without interaction (solution and nozzle). A model comparison was made with **bayesfactor_models** from "bayestestR" package[@makowski2019] to investigate interaction significance. For all response variables (Dvs, RS and % drifable fines), the best model was with interaction. The posterior summaries and treatment means were estimated and compared using Bayes Factor (BF) as above-mentioned.

### 2021-07-15 manuscript.tex
bv

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Spray particle drift},
  pdfauthor={Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo Werle},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin = 2.54cm]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage[left]{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Spray particle drift}
\author{Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo
Werle}
\date{2021-07-14}

@@

@@

\hypertarget{experimental-sites}{%
\subsection{Experimental sites}\label{experimental-sites}}

Field experiments were conducted in three locations: North Platte, NE
(geographic coordinates) on September 11-12/2021; Arlington, WI
(geographic coordinates) on September 15-16/2021; and city, MO
(geographic coordinates) on September 18-20/2021. In NE, WI, and MO,
applications were made on bare ground, corn stubble (XX cm height) and
????, respectively. The fields were flat and with no surrounding trees.
Samples were processed and analyzed at the Pesticide Application
Technology Laboratory of the University of Nebraska-Lincoln located in
North Platte, Nebraska.

@@

\hypertarget{application-and-field-layout}{%
\subsection{Application and field
layout}\label{application-and-field-layout}}

@@

\hypertarget{dye-quantification}{%
\subsection{Dye quantification}\label{dye-quantification}}

@@

@@

\hypertarget{spray-solution-deposition-at-upwind-and-inswath}{%
\subsubsection{Spray solution deposition at upwind and
inswath}\label{spray-solution-deposition-at-upwind-and-inswath}}

@@

\hypertarget{spray-solution-deposition-at-downwind}{%
\subsubsection{Spray solution deposition at
downwind}\label{spray-solution-deposition-at-downwind}}

@@

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within an experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from the ``agricolae'' package. The
AUC is commonly used for plant disease progress\textsuperscript{5,6} but
has been used to calculate herbicide injury.\textsuperscript{7} Data was
fitted to a mixed model using \emph{brm} function. Treatments were the
fixed effects and blocks nested within location random effects. Model
family was gaussian and prior distribution was set to student-t with
mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
summaries (mean and highest posterior density) were estimated with
\emph{emmeans} function from the ``emmeans'' package. Treatment means
were compared using Bayes Factor (BF) as above-mentioned.

\hypertarget{dv-relative-span}{%
\subsubsection{Dv, Relative Span}\label{dv-relative-span}}

@@

\hypertarget{dv-relative-span-1}{%
\subsection{Dv, Relative Span}\label{dv-relative-span-1}}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Off-target spray particle movement},
  pdfauthor={Rodrigo Werle; Bruno C Vieira; Maxwel C. Oliveira; Guilherme Alves; Greg Kruger},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin = 2.54cm]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage[left]{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Off-target spray particle movement}
\author{Rodrigo Werle \and Bruno C Vieira \and Maxwel C.
Oliveira \and Guilherme Alves \and Greg Kruger}
\date{2021-07-15}

@@

Integrate pest management The off-target particle movement

The objective of this stu

@@

@@

\hypertarget{application-and-field-layout}{%
\subsubsection{Application and field
layout}\label{application-and-field-layout}}

@@

\hypertarget{dye-quantification}{%
\subsubsection{Dye quantification}\label{dye-quantification}}

@@

\hypertarget{greenhouse-study}{%
\subsection{Greenhouse study}\label{greenhouse-study}}

A completely randomized design

@@

\hypertarget{field-study-1}{%
\subsubsection{Field study}\label{field-study-1}}

\hypertarget{spray-solution-deposition-at-upwind-and-inswath}{%
\paragraph{Spray solution deposition at upwind and
inswath}\label{spray-solution-deposition-at-upwind-and-inswath}}

@@

\hypertarget{spray-solution-deposition-at-downwind}{%
\paragraph{Spray solution deposition at
downwind}\label{spray-solution-deposition-at-downwind}}

@@

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within an experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from the ``agricolae'' package. The
AUC is commonly used for plant disease progress\textsuperscript{5,6} but
has been used to calculate herbicide injury.\textsuperscript{7} Data was
fitted to a mixed model using \emph{brm} function. Treatments were the
fixed effects and blocks nested within location random effects. Model
family was gaussian and prior distribution was set to student-t with
mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
summaries and treatment means were estimated and compared using Bayes
Factor (BF) as above-mentioned.

\hypertarget{greenouse-study}{%
\subsection{Greenouse study}\label{greenouse-study}}

The Dv(10,50,90), RS, and \% drifable fines was fitted to a Bayesian
linear mixed model using \emph{brm} function. In the models, solution
and nozzle were set as fixed effects. Model family was hurdle gamma and
prior distribution was set to student-t with mean 0.5, standard
deviation 1 and 2 degrees of freedom. For each response variable, two
models were fitted: with and without interaction (solution and nozzle).
A model comparison was made with \textbf{bayesfactor\_models} from
``bayestestR'' package\textsuperscript{8} to investigate interaction
significance. For all response variables (Dvs, RS and \% drifable
fines), the best model was with interaction. The posterior summaries and
treatment means were estimated and compared using Bayes Factor (BF) as
above-mentioned.

@@

\hypertarget{dv-relative-span}{%
\subsection{Dv, Relative Span}\label{dv-relative-span}}

@@

\leavevmode\hypertarget{ref-makowski2019}{}%
\CSLLeftMargin{8 }
\CSLRightInline{Makowski D, Ben-Shachar M, and Lüdecke D, {bayestestR}:
{Describing Effects} and their {Uncertainty}, {Existence} and
{Significance} within the {Bayesian Framework}, \emph{JOSS}
\textbf{4}:1541 (2019).}
